Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-15 examples_C.tex
+

  /*reading page table entry Justified by virtual pte-pointsto*/
  if (!entry->present(*\label{line:read_entry_contents}*)) {/* Jump if the present bit is not zero; no need to allocate next level (* \label{line:check_entry_present} *)(* \label{line:mask_present} *) */
    /*Store the value of rbp minus 16 bytes (address of (*\textsf{next}*)) into rdi (*\label{line:pass_addrof_next}*)(*\label{line:alloc_path_start}*) */

>>>>

  /*Reading page table entry justified by virtual pte-pointsto*/
  if (!entry->present(*\label{line:read_entry_contents}*)) {
    /* Jump if the present bit is not zero; no need to allocate next level (* \label{line:check_entry_present} *)(* \label{line:mask_present} *) */
    /*Allocation path starts here (*\label{line:pass_addrof_next}*)(*\label{line:alloc_path_start}*)*/
